quollr: An R Package for Visualizing $2-\\text{D}$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-08 paper-quollr.Rmd
Added main function intro

@@

The mains steps for the algorithm can be executed by the main function `fit_highd_model()`, or can be run separately for more flexibility. When constructing the $2\text{-}D$ model, the user can choose either to fit the $2\text{-}D$ model with hexagonal bin centroids or bin means using `is_bin_centroid` argument.

If a user would like to perform steps of the algorithm themselves, additional user input will be needed for the function that perform each step. For example, if the user wishes to use already binning data, the `extract_hexbin_centroids()` function can be used directly.

The number of bins along the x-axis, the ratio of the ranges of the original embedding components, the buffer amount as a proportion of data, and if `is_rm_lwd_hex = TRUE`, benchmark value to remove low density hexagons are parameters that will be determined within `fit_highd_model()`, if they are not provided. They are created as they are needed throughout the following example. The function `fit_highd_model()` provides the fitted model in $2\text{-}D$, and $p\text{-}D$.

```{r, echo=TRUE}
fit_highd_model(
  highd_data = s_curve_noise_training,
  nldr_data = s_curve_noise_umap_scaled, 
  bin1 = 12, 
  r2 = r2,
  q = 0.1,
  is_bin_centroid = TRUE
  )
```

>>>>

### Main function

The mains steps for the algorithm can be executed by the main function `fit_highd_model()`, or can be run separately for more flexibility.

<!-- If a user would like to perform steps of the algorithm themselves, additional user input will be needed for the function that perform each step. For example, if the user wishes to use already binning data, the `extract_hexbin_centroids()` function can be used directly. -->

This function requires several parameters: the high-dimensional data (`highd_data`), the emdedding data (`nldr_data`), the number of bins along the x-axis (`bin1`), the buffer amount as a proportion of data (`q`), and benchmark value to extract high density hexagons (`benchmark_highdens`). The function returns an object that includes the hexagonal object, the fitted model in both $2\text{-}D$, and $p\text{-}D$, and triangular mesh.

```{r, echo=TRUE}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  bin1 = 15, 
  q = 0.1, 
  benchmark_highdens = 5)
```

@@
